Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-03 paper/main.tex
polishing Tables 1 and 2 with Terka

\begin{table}[t]
  \caption{Considered translators and the numbers of \emph{fails} and
    successfully constructed automata with \emph{at most 1 mark} and
    with \emph{at least 2 marks} for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%
\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{366 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela -D1} & (2.2.0)\footnotemark[2]
  & ? & ? & \textbf{?} & ? & ? & \textbf{?}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
       & 5 & 214 & \textbf{129} & ? & ? & \textbf{?} \\
  \texttt{ltl2dgra} & (21.0)\footnotemark[3]
       & 12 & 102 & \textbf{234} & ? & ? & \textbf{?}\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[t]
  \caption{The cumulative numbers of acceptance marks before and after
    reduction for various reduction levels and automata sets given by
    the translator and formula set. The column \emph{reduction} shows
    the cumulative percentage of saved acceptance marks and
    \emph{time} reports the cumulative reduction time. The column
    \textit{solver timeout} indicates the number of instances where
    the last call to the QBF solver timed out.  }
\label{tab:cumm-data}
\centering
\setlength{\tabcolsep}{3.9pt}
\newcommand{\mybox}[1]{\fbox{\begin{minipage}{4.7cm}\centering#1\end{minipage}}}
\begin{tabular}{lcrrrrrrrr}
  \toprule
  && \multicolumn{4}{c}{\makecell{reduction of automata from\\[-.8ex] formulas from literature}}
  & \multicolumn{4}{c}{\makecell{reduction of automata from\\[-.8ex] random formulas}}
  \\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
  translator & \makecell{reduction\\[-1ex] level}
  & marks & \makecell{reduction\\[-1ex] [\%]} & \makecell{time\\[-1ex] [s]} & \makecell{solver\\[-1ex] timeout} 
  & marks & \makecell{reduction\\[-1ex] [\%]} & \makecell{time\\[-1ex] [s]} & \makecell{solver\\[-1ex] timeout} \\
  \midrule
%  \multirow{5}{*}{\makecell{\texttt{ltl2tgba -G}}} &
  \multicolumn{2}{l}{\texttt{ltl2tgba -G}} 
  & \multicolumn{4}{c}{\mybox{198 marks in 70 automata}}
  & \multicolumn{4}{c}{\mybox{XYZ marks in XYZ automata}}\\
  & 1
  & 198 & 0.0~~~ & 49.3 & 0~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & 2
  & 198 & 0.0~~~ & 78.9 & 0~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & 3
  & 189 & 4.5~~~ & 1222.8 & 7~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & multi
  & 189 & 4.5~~~ & 1259.1 & 6~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                    
  \midrule
%  \multirow{5}{*}{\makecell{\texttt{ltl2tgba -G}}} &
  \multicolumn{2}{l}{\texttt{ltl3tela}} 
  & \multicolumn{4}{c}{\mybox{348 marks in 91 automata}}
  & \multicolumn{4}{c}{\mybox{XYZ marks in XYZ automata}}\\
  & 1
  & 332 & 4.6~~~ & 465.9 & 12~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & 2
  & 334 & 4.0~~~ & 553.9 & 15~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & 3
  & 326 & 6.3~~~ & 691.8 & 18~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & multi
  & 323 & 7.2~~~ & 1545.9 & 18~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                    
  \midrule
  &&&& \vdots \\
% \\
% level 1 &
% 387~ & 26.0~~~~~~ & 755.4~ &  18~~~
% \\
% &
% level 2 &
% 390~ & 25.4~~~~~~ & 1024.5~ &  20~~~
% \\
% &
% level 3 &
% 393~ & 24.9~~~~~~ & 7273.3~ &  25~~~
% \\
% &
% multi &
% 371~ & 29.1~~~~~~ & 9111.4~ &  21~~~
% \\
% \midrule
% \multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
% &
% level 1 &
% 552~ & 37.4~~~~~~ & 738.7~ & 14~~~
% \\
% &
% level 2 &
% 569~ & 35.5~~~~~~ & 907.3~ &  18~~~
% \\
% &
% level 3 &
% 561~ & 36.4~~~~~~ & 1163.4~ &  21~~~
% \\
% &
% multi &
% 542~ & 38.5~~~~~~ & 2320.7~ &  21~~~
% \\
% \midrule
% \multirow{4}{*}{\makecell{\texttt{ltl3tela}\\91 automata\\348 acc.~marks}}
% &
% level 1 &
% 332~ & 4.6~~~~~~ & 465.9~ &  12~~~
% \\
% &
% level 2 &
% 334~ & 4.0~~~~~~ & 553.9~ &  15~~~
% \\
% &
% level 3 &
% 326~ & 6.3~~~~~~ & 691.8~ &  18~~~
% \\
% &
% multi &
% 323~ & 7.2~~~~~~ & 1545.9~ & 18~~~
% \\
\bottomrule                                                                     
\end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \caption{Considered translators and the numbers of \emph{fails} and
    successfully constructed automata with \emph{at most 1 mark} and
    with \emph{at least 2 marks} for each translator and set of
    formulas.}
\label{tab:ltltranslators}
\centering
% \begin{tabular}{lr@{~~~~~~}lr}
% \toprule
% tool        & version&homepage & ~~~automata \\
% \midrule
% \texttt{ltl2dela}~~~ & 21.0 & \multirow{2}{*}{\url{https://owl.model.in.tum.de/}} & 129\\
% \texttt{ltl2dgra} & 21.0 & & 234\\
% \texttt{ltl2tgba} & 2.10.4 & \url{https://spot.lrde.epita.fr} & 70\\
% \texttt{ltl3tela} & 2.2.0  & \url{https://github.com/jurajmajor/ltl3tela} & 91\\
% \bottomrule
% \end{tabular}
%
% \begin{tabular}{lrrrr}
%   \toprule
%   &&& \multicolumn{2}{c}{constructed automata with} \\ \cmidrule(lr){4-5}
%   tool &\!\!\!version/homepage & ~~~~fails & less than 2 marks & \textbf{at least 2 marks}\\
%   \midrule
%   \texttt{ltl2dela} & 21.0\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
%        & 5 & 214 & \textbf{129} \\
%   \texttt{ltl2dgra} & 21.0\footnotemark[1]
%        & 12 & 102 & \textbf{234}\\
%   \texttt{ltl2tgba} & 2.10.4\tablefootnote{\url{https://spot.lrde.epita.fr}}
%        & 0 & 278 & \textbf{70}\\
%   \texttt{ltl3tela} & 2.2.0\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
%        & 18 & 239 & \textbf{91}\\
%   \bottomrule
% \end{tabular}
%
\setlength{\tabcolsep}{5.7pt}
\begin{tabular}{lrrrrrrr}
  \toprule
  && \multicolumn{3}{c}{\!348 formulas from literature\!} & \multicolumn{3}{c}{366 random formulas}\\
  \cmidrule(lr){3-5} \cmidrule(lr){6-8}
  &&& \multicolumn{2}{c}{automata with} && \multicolumn{2}{c}{automata with}\\
  \cmidrule(lr){4-5} \cmidrule(lr){7-8}
  \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}
  & ~~~~fails & \makecell[r]{at most\\[-1ex] 1 mark} & \makecell[r]{\textbf{at least}\\[-1ex] \textbf{2 marks}}\\
  % &&& at most & \textbf{at least} && at most & \textbf{at least}\\[-.8ex]
  % \multicolumn{2}{l}{translator ~~~ (version)$^{\text{web}}$} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks} & ~~~~fails & 1 mark & \!\!\!\!\textbf{2 marks}\\
  \midrule 
  \texttt{ltl2tgba -G} & (2.10.4)\tablefootnote{\url{https://spot.lrde.epita.fr}}
  & 0 & 278 & \textbf{70} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela} & (2.2.0)\tablefootnote{\url{https://github.com/jurajmajor/ltl3tela}}
  & 18 & 239 & \textbf{91} & ? & ? & \textbf{?}\\
  \texttt{ltl3tela -D1} & (2.2.0)\footnotemark[2]
  & ? & ? & \textbf{?} & ? & ? & \textbf{?}\\ 
  \texttt{ltl2dela} & (21.0)\tablefootnote{\label{fn:owl}\url{https://owl.model.in.tum.de/}}
  & 5 & 214 & \textbf{129} & ? & ? & \textbf{?}\\
  \texttt{ltl2dgra} & (21.0)\footnotemark[3]
  & 12 & 102 & \textbf{234} & ? & ? & \textbf{?}\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[t]
  \caption{The cumulative numbers of acceptance marks before and after
    reduction for various reduction levels and automata sets given by
    the translator and formula set. The column \emph{reduction} shows
    the cumulative percentage of saved acceptance marks and
    \emph{time} reports the cumulative reduction time. The column
    \textit{solver timeout} indicates the number of instances where
    the last call to the QBF solver timed out.  }
\label{tab:cumm-data}
\centering
\setlength{\tabcolsep}{3.9pt}
\newcommand{\mybox}[1]{\fbox{\begin{minipage}{4.7cm}\centering#1\end{minipage}}}
\begin{tabular}{lcrrrrrrrr}
  \toprule
  && \multicolumn{4}{c}{\makecell{reduction of marks in automata\\[-.8ex] from formulas from literature}}
  & \multicolumn{4}{c}{\makecell{reduction of marks in automata\\[-.8ex] from random formulas}}
  \\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
  translator & \makecell{reduction\\[-1ex] level}
  & marks & \makecell{reduction\\[-1ex] [\%]} & \makecell{time\\[-1ex] [s]} & \makecell{solver\\[-1ex] timeout} 
  & marks & \makecell{reduction\\[-1ex] [\%]} & \makecell{time\\[-1ex] [s]} & \makecell{solver\\[-1ex] timeout} \\
  \midrule
%  \multirow{5}{*}{\makecell{\texttt{ltl2tgba -G}}} &
  \multicolumn{2}{l}{\texttt{ltl2tgba -G}} 
  & \multicolumn{4}{c}{\mybox{198 marks in 70 automata}}
  & \multicolumn{4}{c}{\mybox{XYZ marks in XYZ automata}}\\
  & 1
  & 198 & 0.0~~~ & 49.3 & 0~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & 2
  & 198 & 0.0~~~ & 78.9 & 0~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & 3
  & 189 & 4.5~~~ & 1222.8 & 7~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                     
  & multi
  & 189 & 4.5~~~ & 1259.1 & 6~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                    
  \midrule
%  \multirow{5}{*}{\makecell{\texttt{ltl2tgba -G}}} &
  \multicolumn{2}{l}{\texttt{ltl3tela}} 
  & \multicolumn{4}{c}{\mybox{348 marks in 91 automata}}
  & \multicolumn{4}{c}{\mybox{XYZ marks in XYZ automata}}\\
  & 1
  & 332 & 4.6~~~ & 465.9 & 12~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & 2
  & 334 & 4.0~~~ & 553.9 & 15~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & 3
  & 326 & 6.3~~~ & 691.8 & 18~~~
  &   ? &   ?~~~ &     ? &  ?~~~ \\                     
  & multi
  & 323 & 7.2~~~ & 1545.9 & 18~~~
  &   ? &   ?~~~ &    ? & ?~~~ \\                    
  \midrule
  &&&& \vdots \\
% \\
% level 1 &
% 387~ & 26.0~~~~~~ & 755.4~ &  18~~~
% \\
% &
% level 2 &
% 390~ & 25.4~~~~~~ & 1024.5~ &  20~~~
% \\
% &
% level 3 &
% 393~ & 24.9~~~~~~ & 7273.3~ &  25~~~
% \\
% &
% multi &
% 371~ & 29.1~~~~~~ & 9111.4~ &  21~~~
% \\
% \midrule
% \multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\234 automata\\882 acc.~marks}}
% &
% level 1 &
% 552~ & 37.4~~~~~~ & 738.7~ & 14~~~
% \\
% &
% level 2 &
% 569~ & 35.5~~~~~~ & 907.3~ &  18~~~
% \\
% &
% level 3 &
% 561~ & 36.4~~~~~~ & 1163.4~ &  21~~~
% \\
% &
% multi &
% 542~ & 38.5~~~~~~ & 2320.7~ &  21~~~
% \\
% \midrule
% \multirow{4}{*}{\makecell{\texttt{ltl3tela}\\91 automata\\348 acc.~marks}}
% &
% level 1 &
% 332~ & 4.6~~~~~~ & 465.9~ &  12~~~
% \\
% &
% level 2 &
% 334~ & 4.0~~~~~~ & 553.9~ &  15~~~
% \\
% &
% level 3 &
% 326~ & 6.3~~~~~~ & 691.8~ &  18~~~
% \\
% &
% multi &
% 323~ & 7.2~~~~~~ & 1545.9~ & 18~~~
% \\
\bottomrule                                                                     
\end{tabular}
\end{table}
